---
title: "hw_06"
author: "LeoFontenot"
date: "12/9/2021"
output:
  pdf_document: default
  html_document: default
---

# 1

## a

```{r}
x = c(110.5, 105.4, 118.1, 104.5, 93.6, 84.1, 77.8, 75.6)
y = c(5.755, 5.939, 6.010, 6.545, 6.730, 6.750, 6.899, 7.862)
my_lm = lm(y ~ x)
summary(my_lm)

```

The estimate of B1 is `r coef(my_lm)`

## b

```{r}
anova(my_lm)

summary(my_lm)
```
**Since the F statistic is larger than the critical value, we can reject the null hyphothesis**

## c

## d

```{r}
resid(my_lm)
```
**Fitted regression line is Y= 10.137455x -0.037175**

## e
```{r}
summary(my_lm)$sigma^2
```

## f
```{r}
predict(my_lm, newdata = data.frame(x=100), interval = "confidence")
```

## g
```{r}
predict(my_lm, newdata = data.frame(x=100), interval = "prediction")
```
**The prediction interval is wider than the confidence interval**

## h
```{r}
x= summary(my_lm)
x$r.squared
```
**The coefficient of determination is the proportion of the variation in the dependent variable that is predictable from the independent variables. It provides a measure of how well observations are replicated by the model. This coefficient is 0.75 meaning that 75% of the time, predictions match observations.**


# 2

```{r}
x = c(1, 2, 3, 4, 5, 6, 7, 8, 9)
y = c(-2.08, -0.72, 0.28, 0.92, 1.20, 1.12, 0.68, -0.12, -1.28)
my_lm2 = lm(y~x)

```

## a

Plot of y ~ x is below

```{r}
plot(x, y)
```
## b
```{r}
my_residuals= resid(my_lm2)
plot(x = x, y = my_residuals)
```
## c

```{r}
my_residuals= resid(my_lm2)
plot(x = y, y = my_residuals)
```
## d
```{r}
plot(x = fitted(my_lm2), y = my_residuals)
```


## e

**The plot against y and y-hat are different.When the residuals are plotted against y does not show that the linear regression model is not good.It is better to plot against x or y-hat.**






